Relationships in the extremes and their influence on competition and coexistence

### 2021-06-22 paper/Paper.Rnw
new fig
added a couple paragraphs to theory and removed from git some files which should not be under version control

@@

%header material for paper
\title{Place title here}
\date{}

@@

\begin{document}
\SweaveOpts{concordance=TRUE}

%The following is where you load in the numeric results that will be embedded in the text
<<eval=T,echo=F,message=F,warning=F>>=
#system(paste("biber", sub("\\.Rnw$", "", current_input())))

@@

@@

\section{Reference code for Jasmin to learn Latex/Sweave}

To get normal text you just type.

To get a paragraph break you leave a blank line, indentation is automatic.

\noindent If you want to remove the indent you use this.

In-line math is always surrounded by dollar signs, $x+1=4$. Even when you just have single variables, like if you say ``the notation we use for synchrony is $x$'', you put the $x$ in dollar signs. The reason is x and $x$ look different, in a way that a mathematician will notice and wonder if they are meant to be different variables.

For quotes, do it ``like this'' not "like this" or else one of the quotes will be backwards.

Some basic math, inline, by example: $x_{11}$, $y^{22}$, $\frac{1+y}{x+3}$, $\sum_{i=1}^N x_x$,
$\alpha$, $\beta$.

There is also display math:
\begin{equation}
x=y+12-z \label{eq_about_x_and_y}
\end{equation}
The ``label'' command allows a textual label for refering to equations later.

The math gets pretty complex. Keep in mind, whatever you want to do, there is a way to do it. We'll save most of that for later.

Now we can refer to equation/expression (\ref{eq_about_x_and_y}). Latex will sort
out equation numbering and insert the correct number labels for you.

You can also refer to any section in the same way: section \ref{section:introduction}, section \ref{section:methods}.

You can include the value of previously loaded R variables in the text, e.g., the value of allregres[1,5] is
\Sexpr{allregres[1,5]}, which can also be given rounded: \Sexpr{round(allregres[1,5],3)}. You can do simple R
on the fly, e.g., allregres[1,5] plus 1 is \Sexpr{allregres[1,5]+1}. 
You should never manually type any results, they should always be autolinks like this.

%Comments are lines starting with %

You make a percent with \%

You can refer to Fig. \ref{fig:random_fig} by its label and latex will number figures and use the correct numbers.
The label is defined below where the figure is placed.

You can refer to Table \ref{tab:random_table} in the same way.

%You can also refer to figures and tables and equations from the sup mat, just prefix the labels
%by SM- in your calls to \ref{}

You can cite like this \cite{Abanetal2006} or this \citep{Abanetal2006} or this \citealp{Abanetal2006}.
You cal also cite books \citep{BurnhamAnderson2002}, of course.

@@

\section{Tables}

%You make tables like this:
\begin{table}[H]
\caption[Summary caption, for table of contents, can be skipped.]{Full caption here.}
\begin{tabular}{llll} %The four ls mean four columns, each left justified. Can use r or c, too.
\hline 
Col 1 header & Col 2 header & Col 3 header & Col 4 header \\
\hline
text & or & numbers & 3.2 \\
or & math & $x+1$ & or \\
even & the & values & of \\
loaded & R & variables & \Sexpr{allregres[1,5]} \\
you & can & round & \Sexpr{round(allregres[1,5],3)} \\ 
\hline
\end{tabular}
\label{tab:random_table}
\end{table}

\section{Figures}

\begin{figure}[!h]
\includegraphics[width=.5\textwidth]{figures/summaryDocFigures/figure8.png}
\caption{Type the caption here.} \label{fig:random_fig}
\end{figure}

>>>>

\DeclareMathOperator{\EX}{E}% expected value
\DeclareMathOperator{\VarX}{var}
\DeclareMathOperator{\CovX}{cov}
\DeclareMathOperator{\mean}{mean}
\DeclareMathOperator{\se}{se}
\DeclareMathOperator{\sd}{sd}
\DeclareMathOperator{\Prob}{P}

@@

%header material for paper
\title{Relationships in the extremes and their influence on competition and coexistence}
\date{}

%Put other possible titles below, commented, and we will select the best one at the end
%Relationships between extreme events and their influence on competition and coexistence

@@

\begin{document}
%\SweaveOpts{concordance=TRUE}

%The following is where you load in the numeric results that will be embedded in the text
<<eval=T,echo=F,message=F,warning=F>>=
system(paste("biber", sub("\\.Rnw$", "", current_input())))

@@

\section{Theory}\label{section:theory}

For pedgogical clarity, we develop each step of the theory both for a simple classical model, 
the lottery model, and in general. The model is as follows. 
%***DAN: Note the inclusion of the model here means we will have to edit the "Model" section of sup mat, since we don't need to intro the model twice. Do later.
Letting $N_i(t)$ denote the population density of species $i=1,2$ at time $t$, and defining $N = N_1(t)+N_2(t)$,
model equations are
\begin{equation}
N_i(t+1)=(1-\delta)N_i(t)+\delta N \frac{B_i(t)N_i(t)}{B_1(t)N_1(t)+B_2(t)N_2(t)}  \label{model_eq}
\end{equation}
for $i=1,2$. Here, $\delta$ is a mortality rate, and $B_i(t)$ is the fecundiity of species $i$ at time $t$. 
The model postulates that individuals die at rate $\delta$ at each time step, and are replaced by juveniles 
in proportion to the reproductive outputs of the two species that year.
For each $i$, we assume the random variables $B_i(t)$ are independent and identically distributed (iid) through
time. We let $B_i = \exp(b_i)$, where $\left(b_1, b_2\right)$ is some bivariate random variable with the properties 
that $b_i$ is normally distributed with mean $\mu_i$ and variance $\sigma^2$. 
We denote $\CovX(b_1, b_2)$ by $\rho$. However, we do \emph{not} assume that $\left(b_1, b_2\right)$ is a 
bivariate normal distribution. We will consider various distributions of $\left(b_1, b_2\right)$ with the above 
properties, corresponding to symmetric and asymmetric tail association cases.
We assume without loss of generality that $\mu_1 \leq \mu_2$, so that species 1 is the weaker competitor.
Note that $N$ is constant through time.

Modern coexistence theory \citep{Chesson_2000} and its recent computational extensions \citep{Ellner_2016,Ellner_2019} 
%***DAN: Search for REF and replace all with appropriate citations
quantify the contributions of 
different mechanisms to species coexistence. But we show in Sup Mat section X
%***DAN: Make this reference to the sup mat an autolink, and write the section
that, for purely temporal variation, only one mechanism relates to tail associations: storage effects. 
We here define storage effects abstractly and then for the lottery model, using an approach and notation
that follows elements of the presentations in \cite{Ellner_2016} and \cite{Ellner_2019} closely (and see
those papers for additional details and explanation). We 
return briefly to other mechanisms of coexistence in the Discussion.
%***DAN: Don't forget to do this. Basically want to say intuitively why tail associations don't influence those,
%though might be worth mentioning that events are getting more extreme. We have studied how *relationships*
%in the extremes influence coexistence, but probably worth studying (or cite papers if it's been done) how changes
%in the commonness and extremeness of extreme events themselves influence coexistence, and for that you'd have
%to also look at the other mechanisms. 
It is assumed that the growth rate $r_i(t)$ of species $i$ can be written as an increasing function of
an environment-dependent factor $E_i(t)$ and as a decreasing function of a competitive pressure, $C_i(t)$.
For the lottery model, we take $E_i(t)=B_i(t)$, henceforth assuming that fecundity depends strictly on
the environment. Competition $C_i(t)$ is taken to be

@@

@@

### 2021-06-22 paper/Paper.tex
added a couple paragraphs to theory and removed from git some files which should not be under version control

\documentclass[letterpaper,11pt]{article}

@@

%***Need to indicate corresponding authors

\usepackage{Sweave}
\begin{document}
\input{Paper-concordance}

@@

@@

\section{Reference code for Jasmin to learn Latex/Sweave}

To get normal text you just type.

To get a paragraph break you leave a blank line, indentation is automatic.

\noindent If you want to remove the indent you use this.

In-line math is always surrounded by dollar signs, $x+1=4$. Even when you just have single variables, like if you say ``the notation we use for synchrony is $x$'', you put the $x$ in dollar signs. The reason is x and $x$ look different, in a way that a mathematician will notice and wonder if they are meant to be different variables.

For quotes, do it ``like this'' not "like this" or else one of the quotes will be backwards.

Some basic math, inline, by example: $x_{11}$, $y^{22}$, $\frac{1+y}{x+3}$, $\sum_{i=1}^N x_x$,
$\alpha$, $\beta$.

There is also display math:
\begin{equation}
x=y+12-z \label{eq_about_x_and_y}
\end{equation}
The ``label'' command allows a textual label for refering to equations later.

The math gets pretty complex. Keep in mind, whatever you want to do, there is a way to do it. We'll save most of that for later.

Now we can refer to equation/expression (\ref{eq_about_x_and_y}). Latex will sort
out equation numbering and insert the correct number labels for you.

You can also refer to any section in the same way: section \ref{section:introduction}, section \ref{section:methods}.

You can include the value of previously loaded R variables in the text, e.g., the value of allregres[1,5] is
-1.16948109243002, which can also be given rounded: -1.169. You can do simple R
on the fly, e.g., allregres[1,5] plus 1 is -0.169481092430019. 
You should never manually type any results, they should always be autolinks like this.

%Comments are lines starting with %

You make a percent with \%

You can refer to Fig. \ref{fig:random_fig} by its label and latex will number figures and use the correct numbers.
The label is defined below where the figure is placed.

You can refer to Table \ref{tab:random_table} in the same way.

%You can also refer to figures and tables and equations from the sup mat, just prefix the labels
%by SM- in your calls to \ref{}

You can cite like this \cite{Abanetal2006} or this \citep{Abanetal2006} or this \citealp{Abanetal2006}.
You cal also cite books \citep{BurnhamAnderson2002}, of course.

@@

\section{Tables}

%You make tables like this:
\begin{table}[H]
\caption[Summary caption, for table of contents, can be skipped.]{Full caption here.}
\begin{tabular}{llll} %The four ls mean four columns, each left justified. Can use r or c, too.
\hline 
Col 1 header & Col 2 header & Col 3 header & Col 4 header \\
\hline
text & or & numbers & 3.2 \\
or & math & $x+1$ & or \\
even & the & values & of \\
loaded & R & variables & -1.16948109243002 \\
you & can & round & -1.169 \\ 
\hline
\end{tabular}
\label{tab:random_table}
\end{table}

\section{Figures}

\begin{figure}[!h]
\includegraphics[width=.5\textwidth]{figures/summaryDocFigures/figure8.png}
\caption{Type the caption here.} \label{fig:random_fig}
\end{figure}

>>>>

\documentclass[letterpaper,11pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

@@

%***Need to indicate corresponding authors
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
%\SweaveOpts{concordance=TRUE}

@@

\section{Theory}\label{section:theory}

For pedgogical clarity, we develop each step of the theory both for a simple classical model, 
the lottery model, and in general. The model is as follows. 
%***DAN: Note the inclusion of the model here means we will have to edit the "Model" section of sup mat, since we don't need to intro the model twice. Do later.
Letting $N_i(t)$ denote the population density of species $i=1,2$ at time $t$, and defining $N = N_1(t)+N_2(t)$,
model equations are
\begin{equation}
N_i(t+1)=(1-\delta)N_i(t)+\delta N \frac{B_i(t)N_i(t)}{B_1(t)N_1(t)+B_2(t)N_2(t)}  \label{model_eq}
\end{equation}
for $i=1,2$. Here, $\delta$ is a mortality rate, and $B_i(t)$ is the fecundiity of species $i$ at time $t$. 
The model postulates that individuals die at rate $\delta$ at each time step, and are replaced by juveniles 
in proportion to the reproductive outputs of the two species that year.
For each $i$, we assume the random variables $B_i(t)$ are independent and identically distributed (iid) through
time. We let $B_i = \exp(b_i)$, where $\left(b_1, b_2\right)$ is some bivariate random variable with the properties 
that $b_i$ is normally distributed with mean $\mu_i$ and variance $\sigma^2$. 
We denote $\CovX(b_1, b_2)$ by $\rho$. However, we do \emph{not} assume that $\left(b_1, b_2\right)$ is a 
bivariate normal distribution. We will consider various distributions of $\left(b_1, b_2\right)$ with the above 
properties, corresponding to symmetric and asymmetric tail association cases.
We assume without loss of generality that $\mu_1 \leq \mu_2$, so that species 1 is the weaker competitor.
Note that $N$ is constant through time.

Modern coexistence theory (REFS) and its recent computational extensions \citep{Ellner_2016,Ellner_2019} 
%***DAN: Search for REF and replace all with appropriate citations
quantify the contributions of 
different mechanisms to species coexistence. But we show in Sup Mat section X
%***DAN: Make this reference to the sup mat an autolink, and write the section
that, for purely temporal variation, only one mechanism relates to tail associations: storage effects. 
We here define storage effects abstractly and then for the lottery model, using an approach and notation
similar to that of \cite{Ellner_2016} and \cite{Ellner_2019}.

@@

@@
